Errata

### 2025-04-05 tex/Manuscript-1.tex
Add auxiliary files and update manuscript sections for biocrust research
- Created auxiliary files for Conclusions, Introduction, Kurzfassung, Methodology, Publications, and Results_Discussion sections.
- Updated the Introduction section with detailed citations and section labels.
- Adjusted formatting in the Manuscript-1.tex file for improved layout and clarity.
- Enhanced Methodology section with comprehensive study site descriptions and experimental methods.
- Structured Results and Discussion section to include detailed findings on biocrust impacts on soil properties and stability.

% NOTE: NO \documentclass, NO \begin{document}, NO \end{document} in this file!
\usepackage{subcaption} % Add this package for subfigure support

@@

>>>>

% NOTE: NO \documentclass, NO \begin{document}, NO \end{document} in this file!

@@

\begin{center}
    \textbf{\Large Manuscript 1}

    \vspace{0.3cm}
    \textit{SOIL, 8, 717–731, 2022}\\
    \textit{DOI: 10.5194/soil-8-717-2022}

    \vspace{0.5cm}

    Nicolás Riveras-Muñoz\textsuperscript{1*}, Steffen Seitz\textsuperscript{1}, Kristina Witzgall\textsuperscript{2}, Victoria Rodríguez\textsuperscript{3}, Peter Kühn\textsuperscript{1}, Carsten W. Mueller\textsuperscript{4}, Rómulo Oses\textsuperscript{5}, Oscar Seguel\textsuperscript{6}, Dirk Wagner\textsuperscript{3,7}, and Thomas Scholten\textsuperscript{1}

    \vspace{0.2cm}
\end{center}

\begin{small}
    \begin{justify}
    \textsuperscript{1} University of Tübingen, Department of Geosciences, Soil Science and Geomorphology, Rümelinstr. 19-23, 72070 Tübingen, Germany

    \textsuperscript{2} Technical University of Munich, Soil Science, Emil-Ramann-Str. 2, 85354 Freising, Germany

    \textsuperscript{3} GFZ German Research Centre for Geosciences, Section 5.3 Geomicrobiology, Telegrafenberg, 14473 Potsdam, Germany

    \textsuperscript{4} Department of Geosciences and Natural Resource Management, University of Copenhagen, Copenhagen, Denmark

    \textsuperscript{5} Universidad de Atacama, Centro Regional de Investigación y Desarrollo Sustentable de Atacama (CRIDESAT), Copayapu 485, Copiapó, Chile

    \textsuperscript{6} Universidad de Chile, Facultad de Ciencias Agronómicas, Av. Santa Rosa \#11315, La Pintana, 8820808 Santiago, Chile

    \textsuperscript{7} University of Potsdam, Institute of Geosciences, Karl-Liebknecht-Str. 24-25, 14476 Potsdam, Germany
    \end{justify}
\end{small}

\vspace{0.5cm}

\begin{center}
    Submitted: March 07, 2022\\
    Accepted: October 22, 2022\\
    Published: December 07, 2022
\end{center}

\cleardoublepage
